Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-14 programlogic.tex
tiny tweaks

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
\todo[inline]{Colin says: I will go back and add some foreshadowing in the explanation of virtual points-to,
which already contains the Aspaces lookup a couple pages back.}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]

@@

In Figure \ref{fig:addrswitch}, we see two different address-spaces rooted at R0 and R1 in the pre/post condition. To be put into words, while switching an address-space by executing \lstinline|mov_ctl|) updating the  \lstinline|cr3|, it is expected to mention resources of two different address-spaces in the specification. In the precondition,  \lstinline|cr3| is loaded with R0 and all the virtual-pointsto assertions $a_0 \mapsto_{\textsf{v}}p_0$ and $a_1 \mapsto_{\textsf{v}}p_1$ are in the current-view of the memory and valid in the ambient logic \textsf{vProp}. The other address-space with the root address R1 has its own resources ($b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$) which are invalid under the current address space rooted at R0. This pattern of specification requires resources being mentioned under the \textit{world} they are valid, i.e. a modal-framing within the specification. Once the current address-space becomes the one with root address R1, i.e.  \lstinline|cr3| is loaded with R1, the context-resources $b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$ are loaded into the current-view of the memory, and all the other resources that are valid under R0 are introduced into the modal context rooted at R0
\begin{figure}
\[
  \begin{array}{l}
    \hbox{(\TirNameStyle{ModalAddressSpace)}} \qquad
         [r](P) \;: \mathsf{vProp} \; \Sigma \; \stackrel{\triangle}{:=} \; \lambda \mathsf{P},\; \mathsf{P r}. 
  \end{array}
  \]
  \label{fig:modaldef}
  \end{figure}

>>>>

\subsection{Address-Space Management}
\label{sec:aspacemanagement}
\todo[inline]{Colin has not looked at this section in detail yet.
It is clear the discussion of the cr3 update needs updating for doubles}
So far, we have introduced logical abstractions for a single address space. However, \textsf{VMM} implementations handle more than one address-space which we abstract as a ghost map from root address of an address-space to a namespace labelling the address space
\[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]

@@

In Figure \ref{fig:addrswitch}, we see two different address-spaces rooted at R0 and R1 in the pre/post condition. To be put into words, while switching an address-space by executing \lstinline|mov_ctl|) updating the  \lstinline|cr3|, it is expected to mention resources of two different address-spaces in the specification. In the precondition,  \lstinline|cr3| is loaded with R0 and all the virtual-pointsto assertions $a_0 \mapsto_{\textsf{v}}p_0$ and $a_1 \mapsto_{\textsf{v}}p_1$ are in the current-view of the memory and valid in the ambient logic \textsf{vProp}. The other address-space with the root address R1 has its own resources ($b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$) which are invalid under the current address space rooted at R0. This pattern of specification requires resources being mentioned under the \textit{world} they are valid, i.e. a modal-framing within the specification. Once the current address-space becomes the one with root address R1, i.e.  \lstinline|cr3| is loaded with R1, the context-resources $b_0 \mapsto_{\textsf{v}}p_3$ and $b_1 \mapsto_{\textsf{v}}p_4$ are loaded into the current-view of the memory, and all the other resources that are valid under R0 are introduced into the modal context rooted at R0
\begin{figure}
\[
  \begin{array}{l}
    \hbox{(\TirNameStyle{ModalAddressSpace)}} \qquad
         [r](P) \;: \mathsf{vProp} \; \Sigma \; \stackrel{\triangle}{:=} \; \lambda \_,\; \mathsf{P}~\mathsf{r}. 
  \end{array}
  \]
  \label{fig:modaldef}
  \end{figure}

### 2023-04-14 soundness.tex
+
tiny tweaks

\section{Implementing Logical Machinery \& Soundness}
We build our program logic, as an instantiation of Iris~\cite{iris}, and construct our reasoning principles including the modal one on top of it. 
\mytodo{we should put some stuff here}
\subsection{Soundness}
\label{sec:soundness}
Our logic, operates on the machine state, which means we do not need to augment the machine state. The invarian that we pick, \textit{central invariant} ($\textsf{x64\_h}$), is just semantic interpretation of stores in the machine state, $\sigma.\mathcal{R}$ and $\sigma.\mathcal{M}$. This semantic interpratation ensures the correct lifting of mappings in the machine state to the assertions that the client of our logic uses, i.e. points-to assertions that are defined as the ownership of a fragment of the logical state.

@@

After obtaining ownership (points-to) predicates from application of state interpretation, now, we have well-enough definition for giving an outline for the proof of \TirNameStyle{WriteToRegFromVirtMem}.
 \begin{lemma}[\textsc{\TirNameStyle{WriteToRegFromVirtMem}}]
   \label{lemma:unlink}
\begin{align*}
\inferrule{
  \{P \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
}{
  \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}
  \textsf{mov}~\textsf{r}_d,~\textsf{r}_a;\;\overline{is}
}
\end{align*}
 \end{lemma}

>>>>

\section{Implementing Logical Machinery \& Soundness}
We build our program logic, as an instantiation of Iris~\cite{jung2018iris}.
\subsection{Soundness}
\label{sec:soundness}
Our logic, operates on the machine state, which means we do not need to augment the machine state. The invarian that we pick, \textit{central invariant} ($\textsf{x64\_h}$), is just semantic interpretation of stores in the machine state, $\sigma.\mathcal{R}$ and $\sigma.\mathcal{M}$. This semantic interpratation ensures the correct lifting of mappings in the machine state to the assertions that the client of our logic uses, i.e. points-to assertions that are defined as the ownership of a fragment of the logical state.

@@

After obtaining ownership (points-to) predicates from application of state interpretation, now, we have well-enough definition for giving an outline for the proof of \TirNameStyle{WriteToRegFromVirtMem}.
 \begin{lemma}[\textsc{\TirNameStyle{WriteToRegFromVirtMem}}]
   \label{lemma:unlink}
\begin{align*}
\inferrule{
  \{P \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
}{
  \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}
  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_a;\;\overline{is}
}
\end{align*}
 \end{lemma}
